Coherent optical association of a single molecule

### 2020-10-23 paper.tex
Update captions

% In additional to the final and the excited state, it is also important to select the an initial atomic state in order to improve the coupling.
\begin{figure}[ht!]
  \includegraphics[width=0.48\textwidth]{fig2.pdf}
  \caption{
    (A) Geometry and polarization of trap and Raman beam relative to the bias magnetic field.
    The tweezer and Raman beam is focused through an objective to define the location of the
    atoms and molecule.
    We use a bias B field of $B_0=8.8 G$ alone the tweezer polarization
    to define the quantization axis.
    As a result, the atoms experiences predominately $\pi$ polarization from the tweezer.
    (B) Molecule formation pulse sequence. The tweezer initially consists of only up leg power.
    When driving the Raman transition, the up leg power is smoothly ramped down and
    the down leg power ramped up over $10\mu s$ while maintaining the total power of the tweezer.
    This minimizes the heating on the atoms due to power fluctuation while maximizes the time
    with maximum Raman Rabi frequency when the up and down leg powers are equal.
    (C) Raman pulse time scan on resonance.
    A decaying Rabi oscillation can be observed proving the coherence of
    the Raman transfer process.
    \label{f-raman}}
\end{figure}

@@

\begin{figure}[t!]
  \includegraphics[width=0.48\textwidth]{fig3.pdf}
  \caption{
    (A) Fitting of Raman detuning scans at different times to a model of Raman transition
    with loss on the atom and molecule state. The combined fit is used to determine
    both the Raman Rabi frequency and the loss rates.
    (B) Two-body atom lifetime of $5.1(11) \mathrm{ms}$
    in $15 \mathrm{mW}$ of trap depth caused by off-resonance photoassociation.
    This is used to improve the fitting of the Raman transfer data.
    Inset: Atomic scattering rate scales as $P_{tweezer}^{2.58}$,
    this is consistent with a two photon scattering process.
    We have not measured a clear dependency of the loss rate on the tweezer detuning.
    (C) Direct measurement of molecule lifetime in $15 \mathrm{mW}$ of trap depth.
    Molecule survival is detected by dissociating back to atoms using a second Raman transition.
    The lifetime is consistent with the $0.1990(90) \mathrm{ms}$
    measured from the Raman transition data.
    The oscillation in the survival is the result of the interference
    between the two Raman pulses with incomplete transfer.
    \label{f-lifetime}}
\end{figure}

>>>>

% In additional to the final and the excited state, it is also important to select the an initial atomic state in order to improve the coupling.
\begin{figure}[ht!]
  \includegraphics[width=0.48\textwidth]{fig2.pdf}
  \caption{
    (A) Geometry and polarization of trap and Raman beam relative to the bias magnetic field.
    The tweezer and Raman beam is focused through an objective to define the location of the
    atoms and molecule.
    We use a bias B field of $B_0=8.8 G$ alone the tweezer polarization
    to define the quantization axis.
    As a result, the atoms experiences predominately $\pi$ polarization from the tweezer.
    (B) Molecule formation pulse sequence. The tweezer initially consists of only up leg power.
    When driving the Raman transition, the up leg power is smoothly ramped down and
    the down leg power ramped up over $10\mu s$ while maintaining the total power of the tweezer.
    This minimizes the heating on the atoms due to power fluctuation while maximizes the time
    with maximum Raman Rabi frequency when the up and down leg powers are equal.
    (C) Raman pulse time scan on resonance.
    A decaying Rabi oscillation can be observed proving the coherence of
    the Raman transfer process.
    Inset: Raman detuning scans at different times showing the resonance frequency.
    This is also fitted to a model of Raman transition
    with loss on the atom and molecule state and is used to determine
    both the Raman Rabi frequency and the loss rates.
    \label{f-raman}}
\end{figure}

@@

\begin{figure}[t!]
  \includegraphics[width=0.48\textwidth]{fig3.pdf}
  \caption{
    (A) Direct measurement of molecule lifetime in $15 \mathrm{mW}$ of trap depth.
    Molecule survival is detected by dissociating back to atoms using a second Raman transition.
    The lifetime is consistent with the $0.1990(90) \mathrm{ms}$
    measured from the Raman transition data.
    The oscillation in the survival is the result of the interference
    between the two Raman pulses with incomplete transfer.
    (B) Two-body atom lifetime of $5.1(11) \mathrm{ms}$
    in $15 \mathrm{mW}$ of trap depth caused by off-resonance photoassociation.
    This is used to improve the fitting of the Raman transfer data.
    Inset: Atomic scattering rate scales as $P_{tweezer}^{2.58}$ on a log-log scale,
    this is consistent with a two photon scattering process.
    We have not measured a clear dependency of the loss rate on the tweezer detuning.
    \label{f-lifetime}}
\end{figure}
